---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r upset, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  error = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# znktest

<!-- badges: start -->
[![R build status](https://github.com/zkamvar/znksillysnail/workflows/R-CMD-check/badge.svg)](https://github.com/zkamvar/znksillysnail/actions)
<!-- badges: end -->


This package documents a strange behavior between {reticulate}, {knitr}, 
{withr}, and {testthat}. 

I was testing [{dovetail}](https://github.com/carpentries/dovetail) and noticed
that there were issues in accessing `reticulate::py` in a knitr document 
rendered within a test loaded in an interactive environment. This package is an 
attempt at a reprex.

## The setup

I wanted to test knitting a document using relative paths, so I did the following:

1. set up temporary directory and populate with two folders, one for input, 
   one for output. This directory would be cleaned up when it's parent process 
   (the test) finished. 
2. symlinked/copied the test rmd document into the input folder
3. use `withr::with_dir()` to test knitting the relative path of the input to the
   relative path of the output. 
   
The above steps are wrapped in two helper functions in 
[`testthat/tests/helper-funs.R`](testthat/tests/helper-funs.R):
`provision_jekyll()` and `knit_jekyll()`. 

The Rmarkdown document loaded {reticulate}, assigned a variable with a python
chunk, shows that variable in both an R chunk and inline chunk.

## The problem

This process errors when the package is loaded with {pkgload}:

```{r plload}
withr::deferred_run()
pkgload::load_all()
py1 <- provision_jekyll("simple-python.Rmd")
knit_jekyll(py1)
```
-----------

When the test helpers a loaded without {pkgload}, they work okay. 

```{r src}
withr::deferred_run()
source("tests/testthat/helper-funs.R")
py1 <- provision_jekyll("simple-python.Rmd")
py1
```

```{r res, comment = ""}
cat(readLines(knit_jekyll(py1)), sep = "\n")
```

Examining the traceback from `rlang::trace_back()` shows the call stack 
differences for chunk vs inline code:

```{r vbsrc}
withr::deferred_run()
pyv <- provision_jekyll("verbose-python.Rmd")
```

```{r vres, comment = ""}
cat(readLines(knit_jekyll(pyv)), sep = "\n")
```
